---
title: "Shiny Application and Reproducible Pitch Project"
author: "Godwin Appiah Assumaning"
date: "March 3, 2016"
output: html_document
runtime: shiny
---

**Instructions**

This peer assessed assignment has two parts. 

First, you will create a Shiny application and deploy it on Rstudio's servers. 

Second, you will use Slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

## Inputs and Outputs

You can embed Shiny inputs and outputs in your document. Outputs are automatically updated whenever inputs change.  This demonstrates how a standard R plot can be made interactive by wrapping it in the Shiny `renderPlot` function. The `selectInput` and `sliderInput` functions create the input widgets used to drive the plot.

```{r, echo=TRUE}
library(HistData)
library(dplyr)
library(GGally)
library(ggplot2)

# loading dataset
data("GaltonFamilies")
gf <- GaltonFamilies

# transform inches to cms
gf <- gf %>% mutate(fh=father*2.54,
                    mh=mother*2.54,
                    mph=midparentHeight*2.54,
                    ch=childHeight*2.54)

# fit different linear models for testing
m1 <- lm(ch ~ mph, data=gf)
m2 <- lm(ch ~ mph + gender, data=gf)
m3 <- lm(ch ~ fh + mh + gender, data=gf)
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package="shiny"),
  options=list(
    width="100%", height=550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.



